Physics-based protein structure prediction and design using the confinement method

### 2013-01-11 Paper/paper.tex
changed paper 11_3

The question that we want to answer here is whether we can rank models submitted by the same group.In all cases, we have calculated the free energy
difference between the native structure and the submitted models as well. 
%Identifying the native state from a set of models is a very easy test, that most metapredictors
%already handle correctly, but it is also a first proof of principle. 
First we choose a protein BVU3908 from Bacteroides vulgatus whose PDB id and CASP target code are
2L01 and T0559 respectively. The native structure of this 69 residue protein was solved using NMR.
The best predictor group for this target was "BAKER-ROSETTASERVER".
We initlally checked similarity between the models submitted by "BAKER-ROSETTASERVER" and discarded two of them from the 
analysis on the basis of being too similar to some of the other models. The GDT\_TS score and rmsd
values as shown in Figure~\ref{fig:T0559} indicate that the model 1 was predicted correctly, 
whereas the order of model 3 and 5 was wrong. The main difference
between the model 3 and the rest of the model is that the orientation of first alpha helix of model 3 is opposite.
On the other hand, as shown in Figure~\ref{fig:T0559} confine and release method not only can differentiate the native 
structure from the submitted models , it can also correctly rank all the models like their The GDT\_TS score.

@@

acid residues long. This method works very well if atleast one of the strcuture in the decoy is good. The main advantage of this method is 
that it does not require any reaction coordinate. An interesting application, that we have developed using this method is per residue

@@

This method can be further used for calculating free energy due to very large conformational change. Another application may be
for the case of ligand binding. It can also be used to distinguish the most stable structure during protein design. Another, important
application may be to study the protein folding kinetics, specially to study the phi value analysis.

>>>>

The question that we want to answer here is whether we can rank models submitted by the same group.In all cases, we have calculated the free energy
difference between the native structure and the submitted models as well. 
%Identifying the native state from a set of models is a very easy test, that most metapredictors
%already handle correctly, but it is also a first proof of principle. 
First we choose a protein BVU3908 from Bacteroides vulgatus whose PDB id and CASP target code are
2L01 and T0559 respectively. The native structure of this 69 residue protein was solved using NMR.
The best predictor group for this target was "BAKER-ROSETTASERVER".
We initlally checked similarity between the models submitted by "BAKER-ROSETTASERVER" and discarded two of them from the 
analysis on the basis of being too similar to some of the other models. The GDT\_TS score and rmsd
values as shown in Figure~\ref{fig:T0559} indicate that the model 1 was predicted correctly, 
whereas the order of model 3 and 5 was wrong. Main difference
between the model 3 and the rest of the model is that the orientation of first alpha helix of model 3 is opposite.
On the other hand, as shown in Figure~\ref{fig:T0559} confine and release method not only can differentiate the native 
structure from the submitted models , it can also correctly rank all the models like their The GDT\_TS score.

@@

acid residues long. This method works very well if atleast one of the strcuture in the decoy is good. Main advantage of this method is 
that it does not require any reaction coordinate. Thus one can calculate the free energy difference between two very different conformations. 
An interesting application, that we have developed using this method is per residue

@@

This method can be further used for calculating free energy due to very large conformational change. Another application may be
for the case of ligand binding. It can also be used to distinguish the most stable structure during protein design. Decompition of 
total free energy into the per residue component help identifying residues that give stability to a particular conformation. 
Another, important application may be to study the protein folding kinetics, specially to study the phi value analysis.
